Abb Analysis

### 2017-02-13 abbDataAnalysis_Script.Rmd
updating models

  mod.ext.host <- glm(str.ext.pref~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
```

@@

  mod.ext.host <- lm(str.ext.prem~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict') + suburb,
                      data=str.data.ic)
  mod.pot.host <- lm(str.pot.prem~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)
```

@@

  mod.str <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[un,])

@@

>>>>

  mod.ext.host <- glm(str.ext.pref~type+as.factor(bedbath)+
                        sub.mrkt+as.factor(host.type)+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
                        sub.mrkt+as.factor(host.type)+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
```

@@

  mod.ext.host.prem <- lm(str.ext.prem~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)
  mod.pot.host.prem <- lm(str.pot.prem~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)
```

@@

  mod.ext.ps <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[ps,])

  mod.ext.os <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[os,])

  mod.ext.mu <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[mu,])

  mod.ext.un <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[un,])

@@

### Moving Window Logit

To better capture the spatial variation in the logit model results, we set up a moving window logit model that estimates a different model at each estimation point on the map.  Before beginning, we import a new suburbs shapefile and trim it to those suburbs with Airbnb properties. 
```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 suburbs.shp <- readShapePoly(paste0(data.path, 'geographic/melbSuburbs.shp'),
                              proj4string=CRS("+init=epsg:4283"),
                              delete_null_obj=TRUE)

 ssubs <- table(str.data.ic$suburb)
 s.subs <- subs[subs$id %in% names(ssubs),]
 s.suburbs <- suburbs.shp[suburbs.shp@data$NAME_2006 %in% names(ssubs),]
 sssubs <- fortify(s.suburbs)

Next we set up the prediction points.  We drap a grid over the entire area and use those points for prediction points.

 # Min, Max and Range
 xmin <- min(s.subs$long)
 xmax <- max(s.subs$long)
 ymin <- min(s.subs$lat)
 ymax <- max(s.subs$lat)
 xrange <- xmax-xmin
 yrange <- ymax-ymin

 # Set Scale
 scale <- mean(xrange, yrange)/100

 # Create estimation points
 est.data <- str.data.ic
 est.points <- createGridPoints(s.suburbs, scale, T)

We then specify the logistic regression model and set the moving window bandwidth.

 ## Set model specification

 pot.mod.spec <- str.pot.pref ~ type + as.factor(bedbath) + 
   I(max.guests / bedrooms) + min.stay + 
   I(cancel.policy == 'Flexible') + 
   I(cancel.policy == 'Strict')

 ext.mod.spec <- str.ext.pref ~ type + as.factor(bedbath) + 
   I(max.guests / bedrooms) + min.stay + 
   I(cancel.policy == 'Flexible') + 
   I(cancel.policy == 'Strict')

 ## Set bandwidth

 k <- 400

The results are estimated with the custom MWL function

 pot.results.all <- mwl(est.data, 
                        est.points, 
                        pot.mod.spec, 
                        k)

 ext.results.all <- mwl(est.data, 
                        est.points, 
                        ext.mod.spec, 
                        k)

  pot.results.ps <- mwl(est.data[ps, ], 
                        est.points, 
                        pot.mod.spec, 
                        k)
   pot.results.os <- mwl(est.data[os, ], 
                        est.points, 
                        pot.mod.spec, 
                        k)

   pot.results.mu <- mwl(est.data[mu, ], 
                        est.points, 
                        pot.mod.spec, 
                        k)

   pot.results.un <- mwl(est.data[un, ], 
                        est.points, 
                        pot.mod.spec, 
                        k)

   ext.results.ps <- mwl(est.data[ps, ], 
                        est.points, 
                        ext.mod.spec, 
                        k)
   ext.results.os <- mwl(est.data[os, ], 
                        est.points, 
                        ext.mod.spec, 
                        k)

   ext.results.mu <- mwl(est.data[mu, ], 
                        est.points, 
                        ext.mod.spec, 
                        k)

   ext.results.un <- mwl(est.data[un, ], 
                        est.points, 
                        ext.mod.spec, 
                        k)

Coefficents are extracted and put into a data.frame

MAKE A FUNCTION BELOW HERE

extrMWLCoef <- function(mwl.results,
                        est.points,
                        names.coef){

 coef.names <- rownames(mwl.results[[1]])

 # Create a list to capture
 coef.list <- list()

 # Create a data.frame to capture
 coef.df <- data.frame(lat=est.points@coords[,2],
                       long=est.points@coords[,1])

 # Loop through and extract coefficients
 for(cn in 1:length(coef.names)){
   coef.list[[cn]] <- lapply(mwl.results, getMWLCoef, coef=coef.names[cn])
   coef.df[ ,ncol(coef.df) + 1] <- unlist(coef.list[[cn]])
 }

 # Add plottable names
 colnames(coef.df)[3:13] <- names.coef

 return(coef.df)

}
```

x.names <- c('intercept', 'house', 'bb11', 'bb21', 'bb31',
                              'bb32', 'bb42', 'guest', 'minstay', 'flex', 'strict')

pra.coef <- extrMWLCoef(pot.results.all,
                        est.points,
                        x.names)
era.coef <- extrMWLCoef(ext.results.all,
                        est.points,
                        x.names)
prp.coef <- extrMWLCoef(pot.results.ps,
                        est.points,
                        x.names)
pro.coef <- extrMWLCoef(pot.results.os,
                        est.points,
                        x.names)
prm.coef <- extrMWLCoef(pot.results.mu,
                        est.points,
                        x.names)
pru.coef <- extrMWLCoef(pot.results.un,
                        est.points,
                        x.names)
erp.coef <- extrMWLCoef(ext.results.ps,
                        est.points,
                        x.names)
ero.coef <- extrMWLCoef(ext.results.os,
                        est.points,
                        x.names)
erm.coef <- extrMWLCoef(ext.results.mu,
                        est.points,
                        x.names)
eru.coef <- extrMWLCoef(ext.results.un,
                        est.points,
                        x.names)
```

Finally, these coefficients are converted to a surface.

makeMWLSurfs <- function(mwl.coefs,
                         est.points){

  # Make capture list
  surf.list <- list()

  mwl.coefs <- mwl.coefs[ ,!names(mwl.coefs) %in% c('lat', 'long')]

 # Create surfaces
  for(sl in 1:ncol(mwl.coefs)){

   # If NAs
   to.cut <- which(is.na(mwl.coefs[,sl]))
   if(length(to.cut) > 0){
     surf.points <- est.points[-to.cut,]
     surf.value <- mwl.coefs[-to.cut, sl]
   } else {
     surf.points <- est.points
     surf.value <- mwl.coefs[ , sl]
   }

   # Surface estimation
   surf.list[[sl]] <- point2Surface(surf.points, 
                                    surf.value,
                                    .01, 
                                    1.5)
  }

  names(surf.list) <- names(mwl.coefs)

return(surf.list)    
}

pra.surfs <- makeMWLSurfs(pra.coef,
                          est.points)
era.surfs <- makeMWLSurfs(era.coef,
                          est.points)

prp.surfs <- makeMWLSurfs(prp.coef,
                          est.points)
pro.surfs <- makeMWLSurfs(pro.coef,
                          est.points)
prm.surfs <- makeMWLSurfs(prm.coef,
                          est.points)
pru.surfs <- makeMWLSurfs(pru.coef,
                          est.points)

erp.surfs <- makeMWLSurfs(erp.coef,
                          est.points)
ero.surfs <- makeMWLSurfs(ero.coef,
                          est.points)
erm.surfs <- makeMWLSurfs(erm.coef,
                          est.points)
eru.surfs <- makeMWLSurfs(eru.coef,
                          est.points)
